%SECCIÓN 3. PREGUNTAS INVESTIGACION
\section{Information Recognizing}
In this section will be described the data domain, the dataset, and the variables recognizing, and the SMART objectives.

 \subsection{The domain of the data.}
 One of the common uses of the business intelligence is oriented to the marketing, because all the organizations needs to know the current state of them, the history of their behavior, the capacity to satisfy the client requests and to increase their competitive.\\
 In this data analysis the dataset used is provided by  \href{http://archive.ics.uci.edu/ml/datasets/Online+Retail}{UCI on the official web site} and it contains some records related with the transactions of a store through a time period.
 \subsection{The Dataset}
  Like the UCI web page says, the dataset contains all the transactions occurring between 01/12/2010 and 09/12/2011 for a UK-based and registered non-store online retail.The company mainly sells unique all-occasion gifts. Many customers of the company are wholesalers, it's made off 541909 records of online retails and is composed by a the next fields.
 \begin{itemize}
  \item{InvoiceNo.} Invoice number. Nominal, a 6-digit integral number uniquely assigned to each transaction. If this code starts with letter 'c', it indicates a cancellation. 
  \item{StockCode.} Product (item) code. Nominal, a 5-digit integral number uniquely assigned to each distinct product. 
  \item{Description.} Product (item) name. Nominal. 
  \item{Quantity.} The quantities of each product (item) per transaction. Numeric.	
  \item{InvoiceDate.} Invoice Date and time. Numeric, the day and time when each transaction was generated. 
  \item{UnitPrice.} Unit price. Numeric, Product price per unit in sterling. 
  \item{CustomerID.} Customer number. Nominal, a 5-digit integral number uniquely assigned to each customer. 
  \item{Country.} Country name. Nominal, the name of the country where each customer resides.
 \end{itemize}
 \subsection{Smart Objectives}
 Check the behavior of the online retails from the past, to establish patterns, tendencies, and behaviors of the market.\\
 This objective must be the of high quality because the stakeholder may use it to take decisions.
